\documentclass{sig-alternate}
%\documentclass{acm_proc_article-sp}
%\documentclass[times, 10pt,twocolumn]{article} 
\pagestyle{empty}
%\usepackage{latex8}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algorithmic}

%\usepackage{algorithm2e}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{url}
\input{macros}

\begin{document}
\title{eXpress: Guided Path Exploration for Regression Test Generation}

\author{
Kunal Taneja$^1$, \hspace{0.05in} Tao Xie$^1$,  \hspace{0.05in} Nikolai Tillmann$^2$,  \hspace{0.05in} Jonathan de Halleux$^2$,   \hspace{0.05in} Wolfram Schulte$^2$\\
       \small{$^1$Department of Computer Science, North Carolina State University, Raleigh, NC, 27695, USA}\\
       \small{$^2$Microsoft Research, One Microsoft Way, Redmond, WA, 98074, USA}\\
       \small{$^1$\{ktaneja, txie\}@ncsu.edu, $^2$\{nikolait, jhalleux, schulte\}@microsoft.com} 
}   
%\vspace{-0.6 in}
\maketitle
\thispagestyle{empty}

\input{abstract}
\input{Introduction}
\input{background}
\input{example}
\input{approach}
\input{implementation}
\input{evaluation}
\input{discussion}
\input{related}
\input{conclusions}

%\input{ExperimentalAnalysis}
\bibliographystyle{abbrv}
%\bibliography{nier} 


\begin{thebibliography}{10}
\begin{scriptsize}

\bibitem{demandDriven}
S.~Anand, P.~Godefroid, and N.~Tillmann.
\newblock Demand-driven compositional symbolic execution.
\newblock In {\em Proc. TACAS}, pages 367--381, 2008.

\bibitem{Apiwattanapong2006AUG}
T.~Apiwattanapong, R.~Santelices, P.~K. Chittimalli, A.~Orso, and M.~J.
  Harrold.
\newblock Matrix: Maintenance-oriented testing requirement identifier and
  examiner.
\newblock In {\em Proc. TAICPART}, pages 137--146, 2006.

\bibitem{burnim}
J.~Burnim and K.~Sen.
\newblock Heuristics for scalable dynamic test generation.
\newblock In {\em Proc. ASE}, pages 443--446, 2008.

\bibitem{exe}
C.~Cadar, V.~Ganesh, P.~M. Pawlowski, D.~L. Dill, and D.~R. Engler.
\newblock Exe: automatically generating inputs of death.
\newblock In {\em Proc. CCS}, pages 322--335, 2006.

\bibitem{Clarke:symbolic}
L.~Clarke.
\newblock {A System to Generate Test Data and Symbolically Execute Programs}.
\newblock {\em IEEE Trans. Softw. Eng.}, 2(3):215--222, 1976.

\bibitem{Dig'06:ECOOP}
D.~Dig, C.~Comertoglu, D.~Marinov, and R.~Johnson.
\newblock Automatic detection of refactorings in evolving components.
\newblock In {\em Proc. ECOOP}, pages 404--428, 2006.

\bibitem{doESE05}
H.~Do, S.~G. Elbaum, and G.~Rothermel.
\newblock Supporting controlled experimentation with testing techniques: An
  infrastructure and its potential impact.
\newblock {\em ESE}, pages 405--435, 2005.

\bibitem{evans:DiffTest07}
R.~B. Evans and A.~Savoia.
\newblock Differential testing: a new approach to change detection.
\newblock In {\em Proc. FSE}, pages 549--552, 2007.

\bibitem{CSE}
P.~Godefroid.
\newblock Compositional dynamic test generation.
\newblock In {\em Proc. POPL}, pages 47--54, 2007.

\bibitem{dart}
P.~Godefroid, N.~Klarlund, and K.~Sen.
\newblock {DART}: directed automated random testing.
\newblock {\em Proc. PLDI}, pages 213--223, 2005.

\bibitem{godefroid:fuzz}
P.~Godefroid, M.~Y. Levin, and D.~A. Molnar.
\newblock In {\em NDSS}, 2008.

\bibitem{howritz:prioritization}
S.~Horwitz.
\newblock Tool support for improving test coverage.
\newblock In {\em Proc. ESOP}, pages 162--177, 2002.

\bibitem{joshi:pretext}
P.~Joshi, K.~Sen, and M.~Shlimovich.
\newblock Predictive testing: Amplifying the effectiveness of software testing.
\newblock In {\em Proc. ESEC-FSE}, pages 561--564, 2007.

\bibitem{king:symex}
J.~C. King.
\newblock {Symbolic Execution and Program Testing}.
\newblock {\em Communications of the ACM}, 19(7):385--394, 1976.

\bibitem{jjli:prioritization}
J.~J. Li.
\newblock Prioritize code for testing to improve code coverage of complex
  software.
\newblock In {\em Proc. ISSRE}, pages 75--84, 2005.

\bibitem{majumdar:hybrid}
R.~Majumdar and K.~Sen.
\newblock Hybrid concolic testing.
\newblock In {\em Proc. ICSE}, pages 416--426, 2007.

\bibitem{DSE}
S.~Person, M.~B. Dwyer, S.~Elbaum, and C.~S. P\v{a}s\v{a}reanu.
\newblock Differential symbolic execution.
\newblock In {\em Proc. FSE}, pages 226--237, 2008.

\bibitem{chianti}
X.~Ren, B.~G. Ryder, M.~Stoerzer, and F.~Tip.
\newblock Chianti: A change impact analysis tool for java programs.
\newblock In {\em Proc. ICSE}, pages 664--665, 2005.

\bibitem{santelices08sep}
R.~A. Santelices, P.~Chittimalli, T.~Apiwattanapong, A.~Orso, and M.~J.
  Harrold.
\newblock Test-suite augmentation for evolving software.
\newblock In {\em Proc. ASE}, pages 218--227, 2008.

\bibitem{cute}
K.~Sen, D.~Marinov, and G.~Agha.
\newblock {CUTE}: a concolic unit testing engine for {C}.
\newblock In {\em Proc. FSE}, pages 263--272, 2005.

\bibitem{taneja08:diffgen}
K.~Taneja and T.~Xie.
\newblock {DiffGen}: Automated regression unit-test generation.
\newblock In {\em Proc. ASE}, pages 407--410, 2008.

\bibitem{taneja09:guided}
K.~Taneja, T.~Xie, N.~Tillmann, J.~de~Halleux, and W.~Schulte.
\newblock Guided path exploration for regression test generation.
\newblock In {\em Proc. ICSE, NIER}, May 2009.

\bibitem{Pex}
N.~Tillmann and J.~de~Halleux.
\newblock Pex-white box test generation for {.{N}{E}{T}}.
\newblock In {\em Proc. TAP}, pages 134--153, 2008.

\bibitem{tillmann05:parameterized}
N.~Tillmann and W.~Schulte.
\newblock Parameterized unit tests.
\newblock In {\em Proc. ESEC/FSE}, pages 253--262, 2005.

\bibitem{voas}
J.~Voas.
\newblock {PIE}: A dynamic failure-based technique.
\newblock {\em TSE}, 18(8):717--727, 1992.

\bibitem{xie05:spectra}
T.~Xie and D.~Notkin.
\newblock Checking inside the black box: Regression testing based on value
  spectra differences.
\newblock In {\em Proc. ICSM}, pages 28--37, 2004.

\bibitem{xie05:checking}
T.~Xie and D.~Notkin.
\newblock Checking inside the black box: Regression testing by comparing value
  spectra.
\newblock {\em TSE}, 31(10):869--883, 2005.

\bibitem{fitnex}
T.~Xie, N.~Tillmann, P.~de~Halleux, and W.~Schulte.
\newblock Fitness-guided path exploration in dynamic symbolic execution.
\newblock In {\em Proc. DSN}, 2009.

\end{scriptsize}
\end{thebibliography}



\end{document}
