
%
%  $Description: Author guidelines and sample document in LaTeX 2.09$
%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

\documentclass{sig-alternate}
\usepackage{url}
%\usepackage{times}
%\usepackage{diagrams}
%\usepackage[all]{xy}
\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{float}
\input{macros}
%\documentstyle[times,art10,twocolumn,latex8]{article}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
\pagestyle{empty}

%-------------------------------------------------------------------------
\begin{document}

\conferenceinfo{ICSE}{'10, May 2-8 2010, Cape Town, South Africa}
\CopyrightYear{2010}
\crdata{978-1-60558-719-6/10/05}


\title{Mining API Mapping for Language Migration}

\author{
Hao Zhong$^{1,2}$\thanks{Corresponding authors}, Suresh Thummalapenta$^4$, Tao Xie$^{4*}$, Lu Zhang$^{2,3*}$, Qing Wang$^{1}$\\
\small{$^1$Laboratory for Internet Software Technologies, Institute of Software, Chinese Academy of Sciences, Beijing, 100190, China}\\
\small{$^2$Key Laboratory of High Confidence Software Technologies (Peking University), Ministry of Education, China}\\
\small{$^3$Institute of Software, School of Electronics Engineering and Computer Science, Peking University, China} \\
\small{$^4$Department of Computer Science, North Carolina State University, Raleigh, NC 27695-8206, USA}\\
\small{zhonghao@itechs.iscas.ac.cn, \{sthumma,txie\}@ncsu.edu,
zhanglu@sei.pku.edu.cn, wq@itechs.iscas.ac.cn}}

\maketitle
\thispagestyle{empty}

\begin{abstract}
To address business requirements and to survive in competing markets,
companies or open source organizations often have to release different versions of their projects
in different languages. Manually migrating projects from one language to
another (such as from Java to C\#) is a tedious
and error-prone task. To reduce manual effort or human errors, tools
can be developed for automatic translation of projects from one
language to another. However, these tools require the knowledge of how
Application Programming Interfaces (APIs) of one language are mapped
to APIs of the other language, referred to as API mapping
relations. In this paper, we propose a novel approach,
called MAM (\textbf{M}ining \textbf{A}PI
\textbf{M}apping), that mines API
mapping relations from one language to another using API client
code. MAM accepts a set of projects each with two versions in
two languages and mines API mapping relations between those two
languages based on how APIs are used by the two versions. These
mined API mapping relations assist in translation of projects from
one language to another. We implemented a tool and
conducted two evaluations to show the effectiveness of MAM. The
results show that our tool mines 25,805 unique mapping relations of
APIs between Java and C\# with more than 80\% accuracy. The results
also show that mined API mapping relations help reduce 54.4\% compilation
errors and 43.0\% defects during translation of projects with an
existing translation tool, called Java2CSharp. The reduction in
compilation errors and defects is due to our new mined mapping
relations that are not available with the existing translation
tool.
\end{abstract}\vspace*{-2ex}
% A category with the (minimum) three required fields
\category{D.2.13 Reusable Software}{Reusable Software}{Reusable libraries}\vspace*{-2ex}
%A category including the fourth, optional field follows...
\terms{API mapping relation, Language migration}\vspace*{-2ex}

\input{body/introduction}
\input{body/mapping}
\input{body/example}\vspace*{-1ex}
\input{body/approach}\vspace*{-1ex}
\input{body/experiment}\vspace*{-1ex}
\input{body/discussion}\vspace*{-1ex}
\input{body/related}\vspace*{-1ex}
\input{body/conclusion}\vspace*{-1ex}

\section*{Acknowledgments}
Hao Zhong is grateful to his advisor, Prof. Hong Mei, for the insightful advice on research during 
his PhD program in Peking University. The authors from Chinese Academy of Sciences are sponsored by the National Basic Research Program of China (973) No. 2007CB310802, the Hi-Tech Research and Development Plan of China (863) No. 2007AA010303, and the National Natural Science Foundation of China No. 90718042. The authors from NCSU are supported in part by NSF grant CCF-0725190, NSF grant CCF-0845272, ARO grant W911NF-08-1-0443, and ARO grant W911NF-08-1-0105 managed by NCSU Secure Open Systems Initiative (SOSI). Lu Zhang is sponsored by the National Basic Research Program of China (973) No. 2009CB320703, the High-Tech Research and Development Program of China (863) No. 2007AA010301, the Science Fund for Creative Research Groups of China No. 60821003, and the National Science Foundation of China No. 90718016.
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{latex8}  % sigproc.bib is the name of the Bibliography in this case

% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns

%\balancecolumns % GM June 2007
% That's all folks!

\end{document}

