\begin{abstract}
\Comment{
During its life cycle, a software system undergoes various changes. Regression testing is the activity of testing these changes made to the software system. In particular, regression testing aims to expose behavioral differences between the original and changed versions of the software system. Regression testing is an important activity to ensure software quality. However, regression testing is one of the most expensive activity during software maintenance. Various approaches that have been proposed in literature focus on reducing the cost of regression testing through test suite prioritization, selection or minimization. However, as these approaches do not specifically aim to test the changed parts of the software systems, many behavioral differences cannot be detected. Other approaches that aim to specifically test the changed parts of a software system are expensive.

In this paper, we present an approach that takes two versions of a software system as input and generates a test suite, which on execution exposes behavioral differences between two versions of the software system. Our approach, inserts additional branches in the source code such that if these branches can be covered behavioral differences can be found between the two versions. Our approach then uses a symbolic-execution-based approach to generate test cases that covers these branches. To make the test generation process efficient, our approach guides the symbolic execution engine to avoid exploring branches that cannot help directly or indirectly in exposing behavioral differences between the two versions of software system.
**Discuss Experimental Results**
}

Regression test generation aims at generating test inputs that can detect behavioral differences between the original and the modified version of a software system. There are a huge number of paths in large software systems because of which white-box test generation techniques are often not scalable to these software systems. However, if our aim is to find behavioral differences between two versions of a software system, many of these paths are not useful in detecting behavioral differences. In this paper, we propose an approach that uses Dynamic Symbolic Execution (DSE) for effective
generation of regression unit tests. In particular, our approach prevents
the search strategy in DSE from exploring irrelevant
paths in the source code and prioritize the flipping
of branches such that behavioral differences can be detected effectively.
**Discuss Preliminary Results**

\end{abstract}