% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
\input{macros}


\pagestyle{empty}
%\usepackage{latex8}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{wrapfig}

%\usepackage{algorithm2e}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{url}
%
\usepackage{makeidx}  % allows for indexgeneration
%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads
\addtocmark{Hamiltonian Mechanics} % additional mark in the TOC


\mainmatter              % start of the contributions
%
\title{eXpress: Guided Path Exploration for Regression Test Generation}%
\titlerunning{eXpress}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Kunal Taneja\inst{1} \and Tao Xie\inst{1}
\and Nikolai Tillmann\inst{2} \and Jonathan de Halleux\inst{2} \and Wolfram Schulte\inst{2}}

\institute{Department of Computer Science, North Carolina State University, Raleigh, NC\\
\email{\{ktaneja,txie\}@ncsu.edu}
\and
Microsoft Research, One Microsoft Way, Redmond, WA\\
\email{\{nikolait, jhalleux, schulte\}@microsoft.com}
}
%\author{
%Kunal Taneja$^1$, \hspace{0.05in} Tao Xie$^1$,  \hspace{0.05in} Nikolai Tillmann$^2$,  \hspace{0.05in} Jonathan de Halleux$^2$,   \hspace{0.05in} Wolfram Schulte$^2$\\
%       \small{$^1$Department of Computer Science, North Carolina State University, Raleigh, NC}\\
%       \small{$^2$Microsoft Research, One Microsoft Way, Redmond, WA,}\\
%       \small{$^1$\{ktaneja, txie\}@ncsu.edu, $^2$\{nikolait, jhalleux, schulte\}@microsoft.com} 
%}   

\maketitle              % typeset the title of the contribution

\thispagestyle{empty}
\begin{sloppy}

\vspace{-1ex}
\input{abstract}
\input{Introduction}
\input{background}
\input{example----}
%\input{problem}
\input{approach}
\input{implementation}
\input{evaluation}
%\input{discussion}
\input{related}
\input{conclusions}
\end{sloppy}
%\input{ExperimentalAnalysis}
\bibliographystyle{abbrv}
%\bibliography{express} 
%\Comment{
\vspace{-0.2 cm}

\begin{thebibliography}{10}
\begin{scriptsize}


\bibitem{demandDriven}
S.~Anand, P.~Godefroid, and N.~Tillmann.
\newblock Demand-driven compositional symbolic execution.
\newblock In {\em Proc. TACAS}, pages 367--381, 2008.

\bibitem{burnim}
J.~Burnim and K.~Sen.
\newblock Heuristics for scalable dynamic test generation.
\newblock In {\em Proc. ASE}, pages 443--446, 2008.

\bibitem{Dig'06:ECOOP}
D.~Dig, C.~Comertoglu, D.~Marinov, and R.~Johnson.
\newblock Automatic detection of refactorings in evolving components.
\newblock In {\em Proc. ECOOP}, pages 404--428, 2006.

\bibitem{doESE05}
H.~Do, S.~G. Elbaum, and G.~Rothermel.
\newblock Supporting controlled experimentation with testing techniques: An
  infrastructure and its potential impact.
\newblock {\em ESE}, pages 405--435, 2005.

\bibitem{evans:DiffTest07}
R.~B. Evans and A.~Savoia.
\newblock Differential testing: a new approach to change detection.
\newblock In {\em Proc. FSE}, pages 549--552, 2007.

\bibitem{CSE}
P.~Godefroid.
\newblock Compositional dynamic test generation.
\newblock In {\em Proc. POPL}, pages 47--54, 2007.

\bibitem{dart}
P.~Godefroid, N.~Klarlund, and K.~Sen.
\newblock {DART}: directed automated random testing.
\newblock {\em Proc. PLDI}, pages 213--223, 2005.

\bibitem{godefroid:fuzz}
P.~Godefroid, M.~Y. Levin, and D.~A. Molnar.
\newblock In {\em Proc. NDSS}, pages 151--166, 2008.

\bibitem{jin10:automated}
W.~Jin, A.~Orso, and T.~Xie.
\newblock Automated behavioral regression testing.
\newblock In {\em Proc. ICST}, 2010.

\bibitem{DSE}
S.~Person, M.~B. Dwyer, S.~Elbaum, and C.~S. P\v{a}s\v{a}reanu.
\newblock Differential symbolic execution.
\newblock In {\em Proc. FSE}, pages 226--237, 2008.

\bibitem{qi-ase10}
D.~Qi, A.~Roychoudhury, and Z.~Liang.
\newblock Test generation to expose changes in evolving programs.
\newblock In {\em Proc. ASE}, pages 397--406, 2010.

\bibitem{santelices08sep}
R.~A. Santelices, P.~Chittimalli, T.~Apiwattanapong, A.~Orso, and M.~J.
  Harrold.
\newblock Test-suite augmentation for evolving software.
\newblock In {\em Proc. ASE}, pages 218--227, 2008.

\bibitem{cute}
K.~Sen, D.~Marinov, and G.~Agha.
\newblock {CUTE}: a concolic unit testing engine for {C}.
\newblock In {\em Proc. FSE}, pages 263--272, 2005.

\bibitem{taneja08:diffgen}
K.~Taneja and T.~Xie.
\newblock {DiffGen}: Automated regression unit-test generation.
\newblock In {\em Proc. ASE}, pages 407--410, 2008.

\bibitem{taneja09:guided}
K.~Taneja, T.~Xie, N.~Tillmann, J.~de~Halleux, and W.~Schulte.
\newblock Guided path exploration for regression test generation.
\newblock In {\em Proc. ICSE, NIER}, May 2009.

\bibitem{Pex}
N.~Tillmann and J.~de~Halleux.
\newblock Pex-white box test generation for {.{N}{E}{T}}.
\newblock In {\em Proc. TAP}, pages 134--153, 2008.

\bibitem{voas}
J.~Voas.
\newblock {PIE}: A dynamic failure-based technique.
\newblock {\em TSE}, 18(8):717--727, 1992.

\bibitem{fitnex}
T.~Xie, N.~Tillmann, P.~de~Halleux, and W.~Schulte.
\newblock Fitness-guided path exploration in dynamic symbolic execution.
\newblock In {\em Proc. DSN}, 2009.

\bibitem{xu-directed}
Z.~Xu and G.~Rothermel.
\newblock Directed test suite augmentation.
\newblock In {\em APSEC}, pages 406--413, 2009.

\end{scriptsize}
\end{thebibliography}



\end{document}
