\section{Test Adequacy Criteria}
\label{sec:mapping}
As stated by Andrews \emph{et al.}~\cite{andrews2003test}, a test adequacy criterion is a predict, and a test suite is adequate with respect to a criterion only if all defined properties of the criterion are satisfied by the test suite. In this paper, we define four test adequacy criteria for API mapping relations as follows.

\textbf{Static field criterion.} Given a static field $f$ of a class $C$ in a language $L_1$ and its mapped interface $\psi(C.f)$ in a language $L_2$, a adequate test suite should reveal all values of $C.f$ with respect to the static field criterion. This criterion ensures that all values of $f$ in $L_1$ is correctly mapped to $\psi(C.f)$ in $L_2$.

\textbf{Non-static field criterion.} Given a non-static field $f$ of a class $C$ in a language $L_1$ and its mapped interface $\psi(obj.f)$ in a language $L_2$, a adequate test suite should reveal all states of $obj$ with respect to the field criterion. This criterion ensures that all states of $obj$ in $L_1$ return the same values with $\psi(obj.f)$ in $L_2$.

\textbf{Static Method criterion.} Given a static method $m(T_1\ p_1,\ldots,$ $T_n\ p_n)$ of a class $C$ in a language $L_1$ and its mapped interface $\psi(C.m(T_1\ p_1,\ldots,T_n\ p_n))$ in a language $L_2$, a adequate test suite should reveal all paths of $m(T_1\ p_1,\ldots,T_n\ p_n)$ with respect to the static method criterion. This criterion ensures that $m(v_1,\ldots,$ $v_n)$ in $L_1$ returns the same values with $\psi(C.m(v_1,\ldots,v_n$ $))$ in $L_2$.

\textbf{Non-static method criterion.} Given a non-static method $m(T_1\ p_1,$ $\ldots,$ $T_n\ p_n)$ of a class $C$ in a language $L_1$ and its mapped interface $\psi(obj.m(T_1\ p_1,\ldots,$ $T_n\ p_n))$ in a language $L_2$, a adequate test suite should reveal all paths of $m(T_1\ p_1,\ldots,$ $T_n\ p_n)$ with respect to the non-static method criterion. This criterion ensures that $obj.m(v_1,\ldots,$ $ v_n)$ in $L_1$ is correctly mapped to $\psi(obj.m(v_1,\ldots,$ $ v_n))$ in $L_2$.

\textbf{Round-trip criterion.} Given two mapped APIs (an API $i_1$ in a language $L_1$, an API $i_2$ in a language $L_2$, $\psi(i_1)=i_2$, and $\psi^{-1}(i_2)=i_1$), a adequate test suite should be adequate to test both the mapping relation $\psi(i_1)=i_2$ and the mapping relation $\psi^{-1}(i_2)=i_1$.
