\begin{abstract}
Code Search Engines (CSE) can serve as powerful resources of open
source code, as they can search in billions of lines of open source
code available on the web. The strength of CSEs can be used for
several tasks like searching relevant code samples, identifying
hotspots, and finding bugs. However, the major limitations in using
CSEs for these tasks are that the returned samples are too many and
they are often partial. Our framework addresses the preceding
limitations and thereby helps in using CSEs for these tasks. We
showed the effectiveness of our framework with two tools developed
based on our framework.

\Comment{CSEs are often used by programmers to search for relevant
code samples from publicly accessible source code. However, CSEs are not quite
helpful in practice because the number of returned samples are too many and
the desired code sample is often not available among the first several results.
Apart from using CSEs for searching relevant code samples, CSEs can also be used
for several other applications like identifying framework hotspots and finding bugs
in software. Exploiting CSEs for these applications requires analysis of
the code samples returned by CSEs. This analysis is non-trivial because the code samples
returned by CSEs are often partial.\Comment{, as CSEs retrieve
only source files with usages of the given query instead of entire projects.}
In this paper, we propose an extensible framework that addresses the preceding limitations
and thereby helps in exploiting CSEs for several applications that can help improve the
productivity of programmers. Our framework performs static analysis over code samples gathered from a CSE by
using several heuristics and transforms those samples into graph representations that can be directly
used for other applications. }
\end{abstract}
