\newcommand{\puttitle}[0]{Testing and Analysis of Access Control Policies}

\title{\puttitle}
% Fill the following information to accurately reflect on title page
% NOTE: if you are a PhD student, fill \degree with Doctor of Philosophy
\author{Evan E. Martin}

%replace degree year with your anticipated degree year
\degreeyear{2009}
\numberofmembers{4}

%See the NCSU style files if you have a co-chair - JSB.
\degree{Doctor of Philosophy}
\chair{Dr. Tao Xie}
\memberIV{Dr.Gregory T. Byrd}
\memberIII{Dr. Munindar P. Singh}
\memberII{Dr. Ting Yu}

\newpage
\thispagestyle{empty}
%Defined construct to puts the word "ABSTRACT" as per requirement...
\abstractname
\vskip .5cm
% EA - The header of the abstract must be single spaced -- add this
% explicitly using \ssp
\ssp
% Use \noindent to ensure the Abstract header is left justified...
\noindent 
Martin, Evan E. \puttitle. (Under the direction of Professor Tao Xie).

\renewcommand{\baselinestretch}{2}

\vspace{0.2in}

% EA - The rest of the document should be double spaced
\dsp

Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  

Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  Abstract goes here.  



% EA - If your abstract runs more than one page you will need
% the following lines to force a page break between paragraphs
% and not put a page number on the second (and subsequent)
% pages of your abstract.
%
%\newpage
%\thispagestyle{empty}
%

% EA - Put your field here:  Physics, Mathematics, Statistics, etc.
\field{Computer Science}

% EA - I added ', North Carolina' per thesis editor's
% directions
\campus{Raleigh, North Carolina}

\maketitle

\begin{frontmatter}

\begin{dedication}
\vskip .5cm
For the patience of my wife, the implicit encouragement of my children.
\end{dedication}

\biographyname
\vskip .5cm
Evan E. Martin received a Ph.D in Computer Science and M.S. in Computer Networking from North Carolina State University in 2009 and 2004, respectively, and a B.S. in Computer Science from the University of North Carolina at Chapel Hill in 2002. His research interests are in software engineering and the testing and analysis of access control policies. He is currently an employee at Google, Inc.

\begin{acknowledgements}
\vskip .5cm
Put your acknowledgements here, some people you may wish to thank: advisors, committee, professors, family, friends, and Santa.

\vskip .5cm

More acknowledgements as needed.
\end{acknowledgements}

\tableofcontents
% MS -- switched the order of list of tables and figures
\newpage
\listoftables
\newpage
\listoffigures

\end{frontmatter}
