
% Tao, in the following, could you add something so that the following policy

% coverage definitions are related to those abstract ones defined in section 3?

\section{Policy Coverage in XACML}
\label{sec:coverage}

In XACML languages, we can see there are three major entities:
policies, rules for each policy, and a condition for each rule. We
define policy coverage as follows:

\begin{itemize}

\item \Intro{Policy hit percentage}. A policy is hit by a request
if the policy is applicable to the request; in other words, all the
conditions in the policy's target are satisfied by the request.
Policy hit percentage is the number of hit policies divided by the
number of total policies.

\item \Intro{Rule hit percentage.} A rule for a policy is hit by a
request if the rule is also applicable to the request; in other
words, the policy is applicable to the request and all the
conditions in the rule's target are satisfied by the request. Rule
hit percentage is the number of hit rules divided by the number of
total rules.

\item \Intro{Condition hit percentage.} The evaluation of the
condition for a rule has two outcomes: true and false, which are
called as the true condition and false condition, respectively. A
true condition for a rule is hit by a request if the rule is
applicable to the request and the condition is evaluated to be true.
A false condition for a rule is hit by a request if the rule is
applicable to the request and the condition is evaluated to be
false. Condition hit percentage is the number of hit true conditions
and hit false conditions divided by twice of the number of total
conditions.

\end{itemize}

Note that a policy has at least one rule but a rule can have no
condition, indicating an implicit condition \CodeIn{true}, which is
always satisfied when the rule is applicable. Therefore, when there
are no conditions defined within the policies under consideration,
the condition hit percentage is always the same as the rule hit
percentage. Normally a policy tester shall be able to generate
requests to achieve 100\% for all three types of policy coverage. In
other words, all the to-be-covered entities defined in the policy
coverage are feasible to be covered in principle; otherwise, those
infeasible parts of policy specifications could be removed like dead
code in programs.

To automate the measurement of policy coverage, we have developed a
measurement tool by instrumenting Sun's open source XACML
implementation~\cite{sun05:xacml}. Sun's implementation facilitates
the construction of a PDP. We instrument several methods throughout
their implementation that collect policy, rule, and condition
information when a policy is loaded into the PDP. Then coverage
information is collected and stored in a singleton as requests are
evaluated by a PDP against the policy under test.

\Comment{ To automate the measurement of policy coverage, we have
developed a measurement tool based on Sun's open source XACML
implementation~\cite{sun05:xacml}, written in Java. Based on Sun's
XACML implementation, we first built a Policy Decision Point (PDP),
which receives an access request and returns an access decision. We
then developed several public methods in a Java class for collecting
runtime coverage and insert some call sites to these methods in
several places in the code of Sun's XACML implementation. When PDP
loads given policies, we insert a method call to collect all the
policies, rules, and conditions in the given policies. Every time
PDP determines that all the conditions in a policy's target are
satisfied, we insert a method call to collect policy hit
information. Every time PDP determines that all the conditions in a
rule's target are satisfied, we insert a method call to collect rule
hit information. Every time PDP determines that a condition for a
rule is evaluated to be true or false, we insert a method call to
collect condition hit information.}

After the PDP returns the decision, we output the coverage
information into a text file, whose name is determined by the names
of given policies; if a text file with the same name exists, the
coverage information in the text file is updated by incorporating
the new coverage information. Therefore, when PDP receives several
requests separately against the same set of policies, the aggregated
coverage information achieved by these requests is collected.
Besides the basic coverage information, we also output the details
of covered entities and their covering requests as well as the
details of uncovered entities. The extra information can help
developers or external tools in generating or selecting requests for
achieving higher policy coverage.
