\section {Background}\vspace*{-2ex}
\label{sec:background} 
We next present definitions of keywords such
as hotspots, templates, hooks, and coldspots that are used in our
approach and other related background information.

%--------------------------------------------------------------------------------------
\textbf{Hotspots, Templates, and Hooks:} 
As described by Pree~\cite{pree:metapatterns} and Flores et
al.~\cite{flores:hotspotter}, hotspots depict an application's
flexibility and proneness to reuse. The foundations of hotspots are
built upon the Open-Closed Principle by Martin~\cite{martic:openclosed}.
The Open-Closed principle encompasses two main definitions: the
``closed'' and the ``open'' parts. The ``open'' parts represent
areas that are flexible and variant, whereas the ``closed'' parts
represent areas that are immutable in the given application. The
``closed'' parts are commonly referred as ``templates'' as they
group the open parts together and the ``open'' parts are referred as
``hooks'' as the users can redefine the behavior of these
parts. The combination of templates and hooks, referred as \Intro{hotspots}, 
supports adherence to the Open-Closed
principle of Martin. These hotspots can serve as starting
points for the users when reusing a given application.

%--------------------------------------------------------------------------------------
\textbf{Coldspots:}
We introduce a new concept called coldspots; these
coldspots are areas (API classes and methods) that are rarely used
by the users. We identify an API as a coldspot, if the API method
is neither directly nor indirectly used by the users. A
direct usage refers to the scenario where the API is directly used
by the users. An indirect usage refers to the scenario where
the users use some other API, which in turn uses the
current API of interest. The consideration of indirect usage helps
to reduce false positives while detecting coldspots. In general,
coldspots serve as caveats for the users as there can be difficulties
in gathering related code examples and are less tested compared
to hotspots.