% THIS IS SIGPROC-SP.TEX - VERSION 3.0
% WORKS WITH V3.1SP OF ACM_PROC_ARTICLE-SP.CLS
% JUNE 2007
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.1SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.1SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@acm.org
%
% For tracking purposes - this is V3.0SP - JUNE 2007

\documentclass{sig-alternate}
\include{macros}
\begin{document}

\title{Automatic Generation of High-Coverage Tests via Mining Gigabytes of Dynamic Traces\titlenote{The majority of the work was done during an internship at Microsoft Research.}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%

\author{Suresh Thummalapenta$^1$, Jonathan de Halleux$^2$, Nikolai Tillmann$^2$, Scott Wadsworth$^3$\\
\small{$^1$Department of Computer Science, North Carolina State University, Raleigh}\\
\small{$^2$Microsoft Research, One Microsoft Way, Redmond}\\
\small{$^3$Microsoft Corporation, One Microsoft Way, Redmond}\\
\small{$^1$sthumma@ncsu.edu, $^2$\{jhalleux, nikolait\}@microsoft.com}, $^3$bwadswor@microsoft.com\\
}

\maketitle
\begin{abstract}
An important aspect of software maintenance is to ensure that the changes made in the new version of software do not introduce new defects. Regression testing is a testing methodology that aims at exposing such defects (if any) introduced in the new version of software. The basis for regression testing is a unit test suite that achieves a high code coverage created on a stable version of software and has an embedded test oracle. In this paper, we present a novel scalable approach that automatically generates unit tests on a given version without requiring any manual efforts. Our approach generates parameterized unit tests via mining dynamic traces recorded during program executions. Our approach next uses dynamic symbolic execution to generate regression tests that achieve a high code coverage of the version of software under analysis. In our evaluations, we show that our approach records $\approx$ 1.5GB (size of corresponding C\# source code) of dynamic traces and generates $\approx$ 500,000 regression tests on two core libraries of .NET 2.0 framework. The generated regression tests covered $27,485$ basic blocks, which are 24.3\% higher than the number of blocks covered by recorded dynamic traces. These statistics show that our approach is scalable and can be used in practice to deal with large real-world applications.
\end{abstract}

\input{introduction}
\input{background}
\input{approach}
\input{eval}
\input{discussion}
\input{related}
\input{conclusion}

\bibliographystyle{abbrv}
\bibliography{ICSEIndustry}

\end{document}
